---
title: "Unit9Postlive"
author: "Aravind Veluchamy"
date: "July 20, 2016"
output: 
 html_document:
      keep_md: true
---
##Visitor Example
##Loading Library and Data
```{r}
library(fpp)
data(visitors)
```
###Plotting Time Series
###Looking at the time series data there is a seasonal trend where the data is where usage is reduces towards the end of each year.Overall the usage has been increasing till the year 2000 and then a slight decrease till 2005 followed by an increase till 2010 where the usage again dips. 
```{r}
plot(visitors)
```
###Classical decomposition of data

```{r}
fitd <- decompose(visitors)
plot(fitd)
```
###The results are consistent with time series.However the decomposition gives seasonal trends,overall trends and random fluctuations in a detailed representation.
###Seasonal Adjusted Data
```{r}
eeadj <- seasadj(fitd)
plot(eeadj)
```
###Adding Outliers and after  recomputing seasonally adjusted data I could not find any noticeable difference except for peak at where the outlier was added
```{r}
Visitors2 <- ts(c(visitors[1:60],visitors[61]+500,visitors[62:240]),start=c(1986,1),frequency=12)
fitd1 <- decompose(Visitors2)
eeadj1 <- seasadj(fitd1)
plot(eeadj1)
```
###Adding a outlier did not really make a difference whether added to the middle or end of the timeseries.
### Using STL to decompose the data
```{r}
fit <- stl(Visitors2, s.window=5)
plot(fit)
```
##Volatility using Stocks
###Installing Tseries and adding library
```{r}
library(tseries)
```
###Downloading URTY stock
```{r}
URTYData <- get.hist.quote('urty',quote="Close")
```
###Calculating Log Returns
```{r}
URTYret <- log(lag(URTYData)) - log(URTYData)
```
###Calculating Volatility Measure
```{r}
URTYvol <- sd(URTYret) * sqrt(250) * 100
```
###Volatility Function
```{r}
get
Vol <- function(d, logrets)
{

	var = 0

	lam = 0

	varlist <- c()

	for (r in logrets) {

		lam = lam*(1 - 1/d) + 1
	
	var = (1 - 1/lam)*var + (1/lam)*r^2

		varlist <- c(varlist, var)

	}

	sqrt(varlist)
}
```
###Volatility Measure
```{r}
volest <- Vol(10,URTYret)
volest2 <- Vol(30,URTYret)
volest3 <- Vol(100,URTYret)
```
###Calculate volatility measure with a continuous lookback window.Plot the results with a volatility curve overlay.
```{r}
plot(volest,type="l")
lines(volest2,type="l",col="Red")
lines(volest3, type = "l", col="blue")
```
